---
title: "M09_activity"
author: "Hannah Valenty"
date: "2024-07-25"
output: html_document
---

```{r}
library(tidyverse)
df <- read.csv('data/credit_data.csv')
head(df)
```

Task 1
```{r}
library(ggcorrplot)
df2 <- df[2:7]
cor_mat <- round(cor(df2), 2)
ggcorrplot(cor_mat, lab=T, type='lower')
```

Yes, there appears to be a multicollinearity issue between limit and rating. They have a correlation of 1, which is well above the threshold of 0.8.


Task 2
```{r}
library(car)
mod0 <- lm(Balance~Income+Limit+Rating+Cards+Age+Education, data=df)
coef(mod0)
vif(mod0)
```

The largest VIF is Rating (229.49), the next model will remove this.

```{r}
mod1 <- lm(Balance~Income+Limit+Cards+Age+Education, data=df)
coef(mod1)
vif(mod1)
```

This rebuilt model is more appropriate, and has all VIF values between 1 and 3 (none over 5 and especially not over 10).


Task 3.A: Prediction Interval
```{r}
df2 <- data.frame(Income=65, Limit=6000, Cards=4,
                  Age=60, Education=10)

predict(mod1, newdata=df2, interval='prediction', level=0.95)
```
With the input predictor values used for the model, the predicted Balance value has a predicted interval between 396.1612 and 1038.811, with 95% confidence. 


Task 3.B: Confidence Interval
```{r}
predict(mod1, newdata=df2, interval='confidence', level=0.95)
```
We are 95% confident that the mean predicted Balance value given the input predictor values will fall within a confidence interval of 689.5073 and 745.4653. This is affirming because the interval is smaller than the predicted interval using the same parameters. 