---
title: "M04_activity"
author: "Hannah Valenty"
date: "2024-07-18"
output: html_document
---

Task 1
```{r}
library(dplyr)
library(ggplot2)

df <- read.csv('WA_Marketing-Campaign.csv')
ggplot(df, aes(x=as.character(Promotion), y=SalesInThousands, fill=as.character(Promotion)))+
  geom_boxplot()
```

Task 2

An ANOVA analysis should be used to compare the variance within the data and across the subsets of values.

Task 3

$H_o: \mu_1 = \mu_2 = \mu_3$
There is no significant difference between the means of the three promotions.

$H_a: \mu_i \neq \mu_j$ (for some i, j)
At least one pair of mean sale values across the three promotions are not equal.

Task 4
```{r}
anova <- aov(SalesInThousands~as.character(Promotion), data=df)
summary(anova)
```
p-value = 6.77e-10 < $\alpha$ = 0.05

We are 95% confident that one of the promotions has a different mean sales value than another and therefore we reject the null hypothesis. 

Task 5

Yes, a post-hoc test would be useful in determining the promotion which yielded the most sales on average, and differed from another mean.
