---
title: "M03_activity"
author: "Hannah Valenty"
date: "2024-07-17"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
df <- read.csv('WA_Marketing-Campaign.csv')
```
Task 1
```{r}
promotion3_data <- subset(df, Promotion==3)
```
1.A
```{r}
#Bootstrapping
mean_calc <- function(x){
  return(mean(x, na.rm = T))
}

boot_means <- replicate(1000, {
boot_data <- sample(promotion3_data$SalesInThousands, replace = TRUE)
mean_calc(boot_data)
})

quantile(boot_means, c(0.025, 0.975))
```
Bootstrap CI: (52.99, 57.81)

Task 1.B
```{r}
t.test(df$SalesInThousands)
```
T test CI: (52.06, 54.87)
Interpretation: We are 95% confident that for all restaurants that adopt promotion three, the mean sales in thousands of dollars is between 52.06 and 54.87.


Task 1.C
Bootstrap CI: 53.03780 57.85138 
T test CI: 52.06025 54.87215

The widths between the two tests are very similar and 

Task 2
```{r}
promo_2_3 <- subset(df, Promotion==2 | Promotion==3)

t.test(SalesInThousands~Promotion, data=promo_2_3)

```
We recommend using promotion three, because we are 95% confident that promo 3 will earn an average of 4.79 to 11.27 thousand more dollars than restaurants using promo 2.