---
title: "M05_activity"
author: "Hannah Valenty"
date: "2024-07-19"
output: html_document
---

Task 1
```{r}
library(dplyr)
library(ggplot2)
df <- read.csv('Books_Data_Clean.csv')
head(df)
```

Visualize data
```{r}
ggplot(df, aes(x=Author_Rating, y=gross.sales, fill = Author_Rating))+
  geom_boxplot()
```

Zoom In
```{r}
ggplot(df, aes(x=Author_Rating, y=gross.sales, fill = Author_Rating))+
  geom_boxplot()+
  ylim(0, 3000)
  
```

ANOVA Test
```{r}
anova <- aov(gross.sales~Author_Rating, data=df)
summary(anova)
```

p-value = 3.03e-11 (very close to zero), therefore reject the null hypothesis.

Hypotheses Tests
```{r}
TukeyHSD(anova, conf.level = 0.95)
plot(TukeyHSD(anova, conf.level = 0.95))
```

Rating Pairs & their Intervals

* Famous-Excellent       (-1082.4068, 1829.659) $\rightarrow$ crosses zero (inconclusive)
* Intermediate-Excellent   (1025.9664, 2333.743) $\rightarrow$ both positive (Intermediate larger)
* Novice-Excellent         (1153.2751, 4915.091) $\rightarrow$ both positive (Novice larger)
* Intermediate-Famous      (-110.1401, 2722.597) $\rightarrow$ crosses zero (inconclusive)
* Novice-Famous             (398.6229, 4922.491) $\rightarrow$ both positive (Novice larger)
* Novice-Intermediate      (-496.0455, 3204.702) $\rightarrow$ crosses zero (inconclusive)


Base on the analysis above we can conclude that there are differences across the rating types. Based on further statistical evidence it can be determined that:

* Intermediate is greater than Excellent
* Novice is greater than Excellent
* Novice is greater than Famous

$\bigstar$ On average the two highest gross sale rating categories include Intermediate followed by Novice. 

Task 2

To test the linear relationships of all variables against gross.sales, I would begin by producing a set of scatterplots for each variable pair. We could add the linear model line within the plots to get an even clearer view. Check the residual values for each relationship and if they fall below a threshold we can consider the strength of the linear relationships (close to -1 and 1 are strong, and close to 0 is weak).
