---
title: "M12 Activity"
author: "Hannah Valenty"
date: "2024-07-31"
output: html_document
---

```{r}
st <- read.csv('data/Startups.csv')
head(st)
```

## Task 1
```{r}
mod_state <- lm(Profit~State, data = st)
summary(mod_state)
```
Model Equation: $\hat{Profit} = 103905 + 14869 * I_{Florida} + 9851 * I_{New York}$


## Task 2.A -- No Interaction
```{r}
library(ggplot2)
ggplot(st, aes(x=R.D.Spend, y=Profit, colour = State))+
  geom_jitter()+
  geom_smooth(method='lm', aes(group=State), se=F)
```

## Task 2.B
```{r}
mod_state_rd <- lm(Profit~State+R.D.Spend, data = st)
summary(mod_state_rd)
```
Model Equation: $\hat{Profit} = 48750 + 0.853*R.D.Spend + 1164*I_{Florida} + 9.597 * I_{New York}$

## Task 2.C

The coefficient of the State of Florida can be interpreted as, Florida start ups making $1164 more than start ups in California when spending nothing on R& D. 

## Task 3.A -- With Interaction
```{r}
mod_inter <- lm(Profit~State*R.D.Spend, data = st)
summary(mod_inter)
```
Model Equation: $\hat{Profit} = 43880 + 0.9284 * R.D.Spend + 9242 * I_{Florida} + 7921 * I_{New York} - 0.1151 * R.D.Spend * I_{Florida} - 0.1153 * R.D.Spend * I_{New York}$

## Task 3.B

* Florida:R.D.Spend coefficient: Every change in R&D for start ups in Florida has a higher average Profit from start ups in California by 0.9284 - 0.1151 (0.8133).

* New York:R.D.Spend coefficient: Every change in R&D for start ups in Florida has a higher average Profit from start ups in California by 0.9284 - 0.1153 (0.8131).


## Task 4
```{r}
st$State <- factor(st$State, level = c('Florida','New York','California'))
# Florida reference
mod_inter <- lm(Profit~State*R.D.Spend, data = st)
summary(mod_inter)
# New York reference
st$State <- factor(st$State, level = c('New York','Florida','California'))
mod_inter <- lm(Profit~State*R.D.Spend, data = st)
summary(mod_inter)
```
State does not seem to be a useful predictor of Profit. For each iteration of State reference variables the state p-values all fall above 0.05. It would be best to remove state from the model.
