---
title: "M08 Activity"
author: "Hannah Valenty"
date: "2024-07-24"
output: html_document
---

Task 0
```{r}
library(tidyverse)
import <- read.csv('data/expectancy.csv')
df <- select(import,Life.expectancy, Adult.Mortality,
infant.deaths,HIV.AIDS,BMI, GDP,Schooling)%>%
na.omit()

head(df)
```

Task 1
```{r}
long <- gather(df, key='predictor', value = 'value',
               infant.deaths, Adult.Mortality, HIV.AIDS,
               BMI, GDP, Schooling)

ggplot(long, aes(x=value, y=Life.expectancy, color=predictor))+
  geom_point()+
  facet_wrap(~predictor, scales='free_x')
```

A linear model seems appropriate for predicting Life.expectancy using only the predictors Adult.Mortality, BMI, and Schooling. If the remaining predictors are transformed they could be considered for the model.


Task 2
```{r}
mod1 <- lm(Life.expectancy~infant.deaths + Adult.Mortality + HIV.AIDS +
               BMI + GDP + Schooling, data=df)

df_pred <- mutate(df, predictions=fitted(mod1),
                  resid=residuals(mod1))
```

Task 2.A: Linearity Assumption
```{r}
ggplot(long, aes(x=value, y=Life.expectancy, color=predictor))+
  geom_point()+
  facet_wrap(~predictor, scales='free_x')
```

Not all predictors satisfy the linearity assumption. Adult mortality, BMI, and Schooling show a linear relationship with the response variable (life expectancy). The remaining variables do not have a linear relationship.


Task 2.B: Independence Assumption & Equal Variance Assumption
```{r}
ggplot(df_pred, aes(x=predictions, y=resid))+
  geom_point()+
  geom_hline(yintercept = 0, color='red')
```

The plot above shows a random pattern of the residuals and no patterns or clumping, which satisfies the independence assumption. Additionally, the equal variance assumption is met as there is no discernible pattern (like a cone), meaning the variability is consistent.


Task 2.C: Normal Population Assumption
```{r}
ggplot(df_pred, aes(sample=resid))+
  stat_qq()+
  stat_qq_line(color='orange')
```

The QQ plot above shows the satisfaction of the normal population assumption. Most of the data points are located very close to the QQ fit line.


Task 3
```{r}
summary(df)
```

The variable which will most benefit from a transformation is the GDP. This predictor has the greatest range in values from a minimum of 33.68 to a maximum of 66346.52. Additionally, when viewing the scatter plot between GDP and life expectancy, the shape is exponential rather than linear. A transformation would adjust this issue as well.
